LAGOS lake depth

### 2020-01-05 figures/00_maps.Rmd
reorder legend

gg_states <- 
  ggplot() + 
    geom_sf(data = study_bbox[2,], alpha = 1, size = 0.6, 
          color = "black", fill = "#1D9DCF") +
    geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
    # geom_sf(data = outline, color = "black", alpha = 0, size = 0.8) +
    # geom_sf(data = hu4, fill = "grey") +
    geom_sf(data = states_focal, fill = "white", color = "black", size = 0.4) + 
    geom_sf(data = dplyr::filter(dt, lake_maxdepth_m < 10), 
            aes(color = maxdepth_class), size = 0.3, alpha = 0.8) +
    geom_sf(data = dplyr::filter(dt, lake_maxdepth_m > 10), 
            aes(color = maxdepth_class), size = 0.45, alpha = 0.8) +
    # scale_color_brewer(palette = "Set1") +
    labs(color = "Max depth (m)") +
    # scale_fill_brewer(palette = "Set2") +
    coord_sf(datum =  NA) +
    theme_void()

@@

ggplot() + 
  geom_sf(data = dt_plot, aes(fill = prop_maxdepth)) + 
  coord_sf(datum = NA) + theme_void()

>>>>

gg_states <- 
  ggplot() + 
    geom_sf(data = study_bbox[2,], alpha = 1, size = 0.6, 
          color = "black", fill = "#1D9DCF") +
    geom_sf(data = states_all, fill = "gray", color = "black", size = 0.3) +
    # geom_sf(data = outline, color = "black", alpha = 0, size = 0.8) +
    # geom_sf(data = hu4, fill = "grey") +
    geom_sf(data = states_focal, fill = "white", color = "black", size = 0.4) + 
    geom_sf(data = dt, aes(color = maxdepth_class), size = 0.3, alpha = 0) +
    scale_color_manual(values = viridisLite::viridis(5)) +
    geom_sf(data = dplyr::filter(dt, lake_maxdepth_m < 10),
            aes(color = maxdepth_class), size = 0.3, alpha = 0.8) +
    geom_sf(data = dplyr::filter(dt, lake_maxdepth_m > 10), 
            aes(color = maxdepth_class), size = 0.3, alpha = 0.8) +
    labs(color = "Max depth (m)") +
    coord_sf(datum =  NA) +
    theme_void()

@@

ggplot() + 
  geom_sf(data = dt_plot, aes(fill = prop_maxdepth)) + 
  labs(fill = "") +
  coord_sf(datum = NA) + theme_void()
